Summary Tables

### 2021-09-29 summary_tables.Rmd
Regen and removing CVD from level3

>>>>

```{r, echo=FALSE, results='hide', message=FALSE}
# Export all health results
health <- list()
measure <- c("ylls", "deaths")
pathway <- c("hb", "pathway_hb")
for (k in measure) { # loop for ylls or deaths
  for (j in pathway) { # loop for hb or pathway_hb
    for (i in names(io[-2])) { # loop for cities
      # Temporal datset
      temp <- io[[i]]$outcomes[[j]][[k]]
      # Population by age, and age-sex
      pop_by_age <- io[[i]]$demographic %>% group_by(age) %>% 
        summarize(pop_age = sum(population))
      pop_by_age_sex <- io[[i]]$demographic %>% group_by(age, sex) %>% 
        summarize(pop_age_sex = sum(population))

      # Long format and adding new variables
      health[[k]][[j]][[i]] <- gather(temp, key = "cause", "measure", 
                                      -sex, -age_cat) %>% 
        mutate(city = i,
               scenario = case_when(
                 grepl("scen1", cause) ~ scen_names[1],
                 grepl("scen2", cause) ~ scen_names[2],
                 grepl("scen3", cause) ~ scen_names[3],
                 grepl("scen4", cause) ~ scen_names[4],
                 grepl("scen5", cause) ~ scen_names[5],
               ),
               level1 = case_when(
                 grepl("all_cause", cause) ~ "L1: All Cause",
                 grepl("inj", cause) ~ "L1: RTI"
               ),
               level2 = case_when(
                 grepl("total_cancer", cause) ~ "L2: Cancer",
                 grepl("CVD", cause) ~ "L2: CVD",
                 grepl("COPD", cause) ~ "L2: Respiratory",
                 grepl("LRI", cause) ~ "L2: Respiratory",
                 grepl("T2D", cause) ~ "L2: Other",
                 grepl("total_dementia", cause) ~ "L2: Other",
                 grepl("Parkinson", cause) ~ "L2: Other",
                 grepl("inj", cause) ~ "L2: RTI"
               ),
               level3 = case_when(
                 grepl("IHD", cause) ~ "L3: IHD",
                 grepl("lung_cancer", cause) ~ "L3: lung_cancer",
                 grepl("COPD", cause) ~ "L3: COPD",
                 grepl("stroke", cause) ~ "L3: stroke",
                 grepl("T2D", cause) ~ "L3: T2D",
                 grepl("LRI", cause) ~ "L3: LRI",
                 grepl("breast_cancer", cause) ~ "L3: breast_cancer",
                 grepl("colon_cancer", cause) ~ "L3: colon_cancer",
                 grepl("endo_cancer", cause) ~ "L3: endo_cancer",
                 grepl("liver_cancer", cause) ~ "L3: liver_cancer",
                 grepl("total_dementia", cause) ~ "L3: total_dementia",
                 grepl("myeloma", cause) ~ "L3: myeloma",
                 grepl("Parkinson", cause) ~ "L3: Parkinson",
                 grepl("head_neck_cancer", cause) ~ "L3: head_neck_cancer",
                 grepl("stomach_cancer", cause) ~ "L3: stomach_cancer",
                 grepl("inj", cause) ~ "L3: RTI"
               ),
               dose = case_when(
                 grepl("_pa_ap_", cause) ~ "PA and AP",
                 grepl("_pa_", cause) ~ "PA",
                 grepl("_ap_", cause) ~ "AP",
                 grepl("_inj", cause) ~ "RTI"
               )
        ) %>% # End mutate 
        left_join(pop_by_age, by = c("age_cat" = "age")) %>% 
        left_join(pop_by_age_sex, by = c("age_cat" = "age", "sex" = "sex")) %>% 
        mutate(measure_100k = measure / pop_age * 100000,
               measeure_100k_sex = measure / pop_age_sex * 100000)

    } # Loop for each city
  } # Loop for each pathway
} # Loop for each measure

# Export ylls HB
write.csv(rbindlist(health$ylls$hb, use.names = T),
            "results/multi_city/health_impacts/ylls_hb_lng.csv", 
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(rbindlist(health$ylls$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/ylls_pathway_hb_lng.csv", 
            row.names = F)
# Export deaths HB
write.csv(rbindlist(health$deaths$hb, use.names = T),
            "results/multi_city/health_impacts/deaths_hb_lng.csv", 
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(rbindlist(health$deaths$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/deaths_pathway_hb_lng.csv", 
            row.names = F)
